\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tabu}
\usepackage{hyperref}
\usepackage[explicit,compact]{titlesec}
\usepackage{xcolor}
\usepackage{parskip}

\titleformat{\section}
	{\normalfont\large\bfseries}
	{}
	{0pt}
	{#1}
	[{\titlerule[1pt]}]

\hypersetup{
	colorlinks,
	allcolors=.,
	urlcolor=blue,
}

\newcommand{\separation}{\multicolumn{1}{c}{} \\}
\pagestyle{empty}

\begin{document}

	\begin{center}
		{\Huge --- Félix Chabot ---}
	\end{center}

	\section{Personal information}
	\begin{tabu} to \textwidth {rX}
		Email: & \href{mailto:fchabot1337@gmail.com}{fchabot1337@gmail.com} \\
		Phone: & (579) 488-1254 \\
		Languages: & French and English \\
		\texttt{git} repository: & \url{https://github.com/Chabam}
	\end{tabu}
	\section{Working experiences}
	\begin{tabu} to \textwidth {r|X}
		\separation{}
		Winter 2020 & {\large \bfseries Junior developer} \\
		Summer 2019 & {

			\textbf{Diffusion Solution Intégrées}

			{\footnotesize Granby, QC}

			Member of a team assigned to the biggest client. All communications were done in English with the client itself.
		} \\

		\separation{}

		Fall 2019 & {
			{\large \bfseries Teacher}

			\textbf{Cégep de Granby}

			{\footnotesize Granby, QC}

			Course building, annual position, working with young adults.
		} \\


		\separation{}
		Fall 2017 & {\large \bfseries Intern developer} \\
		Summer 2018 & {
			\textbf{Diffusion Solution Intégrées}

			{\footnotesize Granby, QC}

			Agile methodology, "full-stack" programming.
		} \\

		\separation{}
		Winter 2017 & {
			{\large \bfseries Intern developer}

			\textbf{CYME International Inc.}

			{\footnotesize St-Bruno-de-Montarville, QC}

			Research and development with web technologies.
		} \\

		\separation{}
		Hiver 2016 & {
			{\large \bfseries Intern developer}

			\textbf{Plastiques Berry Canada Inc.}

			{\footnotesize Waterloo, QC}

			Development from A to Z of an intranet web application in \textit{MVC.net}.
		} \\
	\end{tabu}

	\section{Education}
	\begin{tabu} to \textwidth {r|X}
		2019 & {
			{\large \bfseries Bachelor of Science in Computer Science}

			Université de Sherbrooke
		} \\

		\separation{}
		2016 & {
			{\large \bfseries Computer Science Technology Diploma}

			Cégep de Granby
		} \\
	\end{tabu}

	\section{Skills}

	\textbf{General skills} \\
	Communication, teamwork, vulgarization, stress management, learning, patience.

	\textbf{Programming languages} \\
	{\ttfamily bash, C, C\#, C++, CSS, HTML, Haskell, Java, JavaScript (ES6), \\ Objective-C, Python, Rust}

	\textbf{Tools} \\
	{\ttfamily AWS, Confluence, Hibernate, IntelliJ, Jira,} \LaTeX{\ttfamily , PyCharm, React, \\ SVN, Spring, Visual Studio, Visual Studio Code, git, node.js, vim}

	\textbf{Databases} \\
	{\ttfamily MySQL, SQLite, SQL Server}

	\section{Projects}
	{\large \bfseries \href{https://vecpad.netlify.com/}{Vecpad}:}
	{\large a linear algebra visualizer in 3D}

	Realized with \href{https://reactjs.org/}{React} and \href{https://threejs.org/}{three.js}, this project is intended to help the students in imaging courses to get familiar with the different concepts of linear algebra using visualizations.

	\bigskip
	{\large \bfseries \href{https://github.com/daniel-junior-dube/comfywm}{Comfy}:}
	{\large a tiling window manager}

	In collaboration with my colleague \textit{Daniel-Junior Dubé}, we created this system component using the programming language \href{https://www.rust-lang.org/}{Rust}. It is compiled and works entirely inside a \texttt{GNU/Linux} environment with the help of the new protocol \href{https://wayland.freedesktop.org/}{Wayland}.

	\bigskip
	{\large \bfseries \href{https://github.com/Chabam/digital-audio-boombox}{Digital-Audio-Boombox}:}
	{\large a terminal audio player}

	This small project is a proof of concept to demonstrate real time systems. This application communicates directly with a system's audio stream using the library \href{http://www.portaudio.com/}{PortAudio}. It is written in \texttt{C++} (with some \texttt{C++17} here and there).

	\section{Interests}
	\begin{itemize}
		\item Music is one of my greatest passions, I recently started learning guitar.
		\item I do a lot of bouldering and sometime some physical conditioning.
		\item To stay up to date I read technical books. I especially like \textit{O'Reilly}!
		\item Like everybody, at the end of the day I enjoy crashing down on my sofa while watching a good series!
	\end{itemize}
\end{document}